First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-06-09 eg6-letters/coherent/dvcs_he4_prl.tex
Finish M.Garcon comments

Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable 
$x_{A}$: $\xi\approx {{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, 
$\nu$ is the energy of the virtual photon, and 
$M_A$ is the nuclei mass. $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally in DVCS. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
\end{align}
with $H_A$ a GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

To ensure the interaction occurred at the partonic level and that the DVCS handbag 
diagram was dominant, we selected events with $Q^{2}$ greater than 
1~GeV$^{2}$. The exclusivity of the coherent DVCS reaction was ensured by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity variables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 3200 events passed all these requirements, their kinematic 
distributions\footnote{We use here and for other results 
$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$ for 
easier comparison with proton data.} are shown in Fig.~\ref{fig:kin-coverage}.

@@

\bibitem{Berger:2001zb} 
  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
  %``Generalized parton distributions in the deuteron,''
  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
  doi:10.1103/PhysRevLett.87.142302
  [hep-ph/0106192].

\bibitem{Cano:2003ju} 
  F.~Cano and B.~Pire,
  %``Deep electroproduction of photons and mesons on the deuteron,''
  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
  doi:10.1140/epja/i2003-10127-x
  [hep-ph/0307231].

\bibitem{Guzey:2005ba} 
  V.~Guzey and M.~Siddikov,
  %``On the A-dependence of nuclear generalized parton distributions,''
  J.\ Phys.\ G {\bf 32}, 251 (2006)
  doi:10.1088/0954-3899/32/3/002
  [hep-ph/0509158].

>>>>

Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable 
$x_{A}$: $\xi\approx {{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, 
$\nu$ is the energy of the virtual photon, and 
$M_A$ is the nuclei mass. $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally in DVCS. We in fact measure 
Compton form factors (CFF), which are complex quantities defined as:
\begin{align}
\begin{split}
\Re e(&\mathcal{H}_{A}) = \\
    &\mathcal{P} 
\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
\end{split} \\
\Im m(&\mathcal{H}_{A}) = - \pi ( H_A(\xi,\xi,t)-H_A(-\xi,\xi,t)),
\end{align}
with $H_A$ a GPD, $\mathcal{P}$ 
the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).

@@

We selected events with $Q^{2}$ greater than 1~GeV$^{2}$ for which the DVCS handbag 
diagram is believed to be dominant. Then the exclusivity of the reaction was ensured by 
applying a set of cuts on the following kinematic variables: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
the $e'^4$He$'$ system, and the angle $\theta$
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The experimental data for the most relevant exclusivity variables and applied
cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
additional details). We also 
rejected events where a $\pi^0$ was identified by the invariant mass of 
two photons. About 3200 events passed all these requirements, their kinematic 
distributions\footnote{We use here and for other results 
$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$ for 
easier comparison with proton data.} are shown in Fig.~\ref{fig:kin-coverage}.

@@

\bibitem{Berger:2001zb} 
  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
  %``Generalized parton distributions in the deuteron,''
  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
  [hep-ph/0106192].

\bibitem{Cano:2003ju} 
  F.~Cano and B.~Pire,
  %``Deep electroproduction of photons and mesons on the deuteron,''
  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
  [hep-ph/0307231].

\bibitem{Guzey:2005ba} 
  V.~Guzey and M.~Siddikov,
  %``On the A-dependence of nuclear generalized parton distributions,''
  J.\ Phys.\ G {\bf 32}, 251 (2006)
  [hep-ph/0509158].
